%=======================================================================%
%
%	DOCUMENT DEFINITION - EUROPEAN STYLE (CLEAN & SIMPLE)
%
%=======================================================================%

\documentclass[10pt,A4]{article}

%------------------------------------------------------------------------
%	ENCODING & LOGIC
%------------------------------------------------------------------------
\usepackage[utf8]{inputenc}
\usepackage{xifthen}

%------------------------------------------------------------------------
%	FONT (Keeping Gillius for the 'nice' look)
%------------------------------------------------------------------------
\usepackage[default]{gillius}
\renewcommand*\familydefault{\sfdefault}
\usepackage[T1]{fontenc}
\usepackage{moresize}
\usepackage{fontawesome}

%------------------------------------------------------------------------%	PAGE LAYOUT
%------------------------------------------------------------------------
\usepackage[a4paper]{geometry}
\geometry{top=1.5cm, bottom=1.5cm, left=1.8cm, right=1.8cm}
\setlength{\parindent}{0mm}

%-----------------------------------------------------------------------
%	PACKAGES
%----------------------------------------------------------------------- 
\usepackage{multicol}
\usepackage{multirow}
\usepackage{array}
\usepackage{graphicx}
\usepackage{tikz}
\usetikzlibrary{shapes, backgrounds}
\usepackage{transparent}
\usepackage{color}

% Colors
\definecolor{complcol}{RGB}{250,150,10}
\definecolor{bgcol}{RGB}{80,80,80}
\definecolor{softcol}{RGB}{220,220,220}
\definecolor{sectcol}{RGB}{0,100,130}

\usepackage[colorlinks, urlcolor=sectcol]{hyperref}

%=======================================================================%
%	CUSTOM COMMANDS
%=======================================================================%

\newcommand{\mpwidth}{\linewidth}

% Section style: European clean
\newcommand{\cvsection}[1]{
  \vspace{12pt}
  {\Large\textbf{\textcolor{sectcol}{\uppercase{#1}}}}
  \vspace{-6pt}
  \nopagebreak
  \textcolor{softcol}{\hrule}
  \vspace{6pt}
}

% Event style: Single column clean
\newcommand{\cvevent}[4]{
  \vspace{4pt}
  \begin{tabular*}{\linewidth}{@{} p{0.8\linewidth} r @{}}
    \textbf{#2} & \textcolor{bgcol}{\small #1} \\
    \textit{#3} & \\
  \end{tabular*}
  \ifvoid\empty#4\else
    \begin{itemize}
      \renewcommand{\labelitemi}{\textcolor{sectcol}{\tiny$\blacksquare$}}
      \setlength{\itemsep}{0pt}
      \setlength{\parskip}{0pt} \setlength{\parsep}{0pt} #4
    \end{itemize}
  \fi
}

% Simple entry style
\newcommand{\cvitem}[2]{
  \vspace{2pt}
  \begin{tabular*}{\linewidth}{@{} p{0.25\linewidth} p{0.75\linewidth} @{}}
    \textcolor{bgcol}{#1} & #2
  \end{tabular*}
}

% Skill dots (optional, but nice)
\newcommand{\skill}[2]{
  \textcolor{bgcol}{#1} \hfill
  \foreach \x in {1,...,5}{%
      \ifnum\x>#2\relax\textcolor{softcol}{$\bullet$}\else\textcolor{complcol}{$\bullet$}\fi%
    }
}

% Icons with text
\newcommand{\icontext}[2]{\mbox{\textcolor{sectcol}{\csname fa#1\endcsname}\hspace{4pt}#2}}

%=======================================================================%
%	DOCUMENT START
%=======================================================================%
\begin{document}

%-----------------------------------------------------------------------
%	HEADER
%-----------------------------------------------------------------------
\begin{center}
  {\Huge \textbf{\uppercase{Francesco Ioli}}} \\
  \vspace{4pt}
  {\large \textcolor{bgcol}{PhD in Environmental and Infrastructure Engineering | Geoinformatics Specialist}} \\
  \vspace{10pt}

  \begin{minipage}{0.9\linewidth}
    \centering
    \icontext{MapMarker}{Milano, Italy} \hfill
    \icontext{Envelope}{\href{mailto:francesco.ioli@polimi.it}{francesco.ioli@polimi.it}} \hfill
    \icontext{Globe}{\href{https://franioli.github.io}{franioli.github.io}} \hfill
    \icontext{Linkedin}{\href{https://www.linkedin.com/in/francesco-ioli-640061160/}{francesco-ioli}}

    \icontext{Github}{\href{https://github.com/franioli}{github.com/franioli}} \hfill
    \icontext{GraduationCap}{\href{https://scholar.google.com/citations?user=hZkC2UMAAAAJ}{Google Scholar}} \hfill
    \icontext{LineChart}{H-Index: 10}
  \end{minipage}
\end{center}

\vspace{10pt}

%-----------------------------------------------------------------------
%	SUMMARY
%-----------------------------------------------------------------------
\cvsection{Professional Profile}
Specialized in photogrammetry and 3D reconstruction in challenging environments, with a focus on alpine glaciers. PhD in Environmental and Infrastructure Engineering (Geoinformatics). Passionate about open-source software, data, and science. Currently focusing on deep learning image matching and UAV-based topographic surveys.

%-----------------------------------------------------------------------
%	EXPERIENCE
%-----------------------------------------------------------------------
\cvsection{Work Experience}

\cvevent{06/2025 - Present}{Post-doctoral Researcher}{CNR IRPI, Institute for Geo-Hydrological Protection}{
  \item Research on photogrammetric monitoring and geohazard assessment. }

\cvevent{10/2024 - 05/2025}{Post-doctoral Researcher}{University of Zurich, Dept. of Geography (Remote Sensing group)}{
  \item Developed automated pipelines for large-scale DEM reconstruction using satellite multi-view stereo
  for geodetic mass balance. }

\cvevent{11/2020 - 07/2024}{PhD Researcher (Cum Laude)}{Politecnico di Milano, DICA (Italy)}{
  \item PhD Thesis: \textit{Multi-temporal and Multi-scale photogrammetry for Alpine Glacier Monitoring}.
  \item Developed \textbf{ICEpy4D}, an image-based pipeline for 4D glacier monitoring.
  \item Contributed to \textbf{Deep-Image-Matching} library for deep learning SfM.
  \item UAV photogrammetry for structural health assessment and crack detection on concrete bridges. }

\cvevent{04/2022 - 07/2022}{Visiting PhD Student}{University of Twente, ITC (Netherlands)}{
  \item Deep learning wide-baseline stereo matching workflow for 4D monitoring of alpine glaciers. }

\cvevent{2020 - 2024}{Teaching Assistant}{Politecnico di Milano}{
  \item \textit{Photogrammetry and UAV surveying} (MSc), \textit{Statistics} (BSc), \textit{GIS} (BSc), \textit{3D modelling for architecture} (BSc).
}

\cvevent{2021 - 2024}{Tutor in Summer Schools}{Politecnico di Milano}{
  \item \textit{Design and Execution of Topographic Surveys for Land Monitoring} @ Belvedere Glacier (IT).
}

\cvevent{2022}{Topographic Consultant}{Prof. Alberto Bianchi / Gini Telecom}{
  \item Technical consultant for legal disputes and UAV surveys for telecommunication antennas. }

%-----------------------------------------------------------------------
%	EDUCATION
%-----------------------------------------------------------------------
\cvsection{Education}

\cvevent{2017 - 2020}{MSc in Environmental and Land Planning Engineering}{Politecnico di Milano}{
  \item Major in Land Monitoring and Diagnostics. Grade: 110L/110. }

\cvevent{2019}{Erasmus Exchange Programme}{Aalto University (Helsinki, Finland)}{}

\cvevent{2014 - 2017}{BSc in Environmental and Land Planning Engineering}{Politecnico di Milano}{
  \item Thesis: Snowpack surveys using UAVs on the Belvedere glacier. Grade: 102/110. }

\cvevent{2022}{Summer School of Alpine Research}{Obergurgl (Austria)}{
  \item \textit{Close Range Sensing Techniques in Alpine Terrain}.
}

%-----------------------------------------------------------------------
%	SKILLS
%-----------------------------------------------------------------------
\cvsection{Skills}

\cvitem{Programming}{
  \textbf{Python} (Expert), \textbf{Matlab} (Advanced), \textbf{C++} (Basic), \textbf{LaTeX}, \textbf{SQL/PostGIS}.
}

\cvitem{Photogrammetry}{
  Agisoft Metashape, Photomodeler, CloudCompare, COLMAP, MicMac, OpenMVG, ODM.
}

\cvitem{Tools}{
  Pytorch, Docker, Git, QGIS, ESRI ArcGIS, RTKLIB, Leica Infinity.
}

\cvitem{Languages}{
  \textbf{Italian} (Mother tongue), \textbf{English} (C1 - IELTS Certificate).
}

\cvitem{Other}{
  UAV Pilot License (EASA A2 Open Category & Critical Scenarios), Driver's License (B).
}

%-----------------------------------------------------------------------
%	PUBLICATIONS & PROJECTS
%-----------------------------------------------------------------------
\cvsection{Selected Publications \& Awards}

\cvevent{2024}{Marie Curie Seal of Excellence}{MSCA Post-doctoral call}{}

\cvevent{2023}{Young Researcher Prize}{Italian Society of Photogrammetry and Remote Sensing (SIFET)}{}

\vspace{4pt}
\begin{itemize}
  \renewcommand{\labelitemi}{\textcolor{sectcol}{\tiny$\blacksquare$}}
  \item \textbf{Ioli, F.} et al. (2024). Deep Learning Low-cost Photogrammetry for 4D Short-term Glacier Dynamics Monitoring. \textit{PFG Journal}.
  \item \textbf{Ioli, F.} et al. (2022). Mid-Term Monitoring of Glacier’s Variations with UAVs. \textit{Remote Sensing}.
  \item \textbf{Morelli, L., Ioli, F.} et al. (2024). Deep-Image-Matching: a Toolbox for Multi-view Image Matching. \textit{ISPRS Archives}.
\end{itemize}

%-----------------------------------------------------------------------
%	ADDITIONAL INFO
%-----------------------------------------------------------------------
\cvsection{Additional Information}

\cvevent{Volunteering}{Diverse Organizations}{2012 - 2024}{
  \item \textit{Apwoyo} (Homeless support), \textit{AGESCI} (Scout Chief), \textit{Libera} (Anti-mafia association).
}

\vfill

\begin{center}
  \footnotesize
  \textit{According to Regulation of the European Parliament 679/2016, I hereby express my consent to process my data for recruiting purposes.} \\
  \vspace{4pt}
  \textcolor{bgcol}{Francesco Ioli --- \today}
\end{center}

\end{document}
