%-------------------------------------------------------------------------------
%	EDUCATION SECTION
%-------------------------------------------------------------------------------
\cvsection{Education}

\cvevent{2020 - 2024}{PhD (Cum Laude)}{Politecnico di Milano, DICA (IT)}{
\href{https://hdl.handle.net/10589/224092}{PhD Thesis}: \textit{Multi-temporal and Multi-scale photogrammetry for Alpine Glacier Monitoring}.\\
Development of novel photogrammetric techniques for territorial and infrastructural monitoring. 
Created \href{https://github.com/franioli/icepy4d}{ICEpy4D}{,} an image-based pipeline for 4D glacier monitoring with low-cost stereo cameras.  
Contributed to \href{https://github.com/3DOM-FBK/deep-image-matching}{Deep-Image-Matching}{,} a multi-view image matching library with deep learning for SfM.
Application of UAV photogrammetry for structural health assessment{,} including crack detection on concrete bridges.
}

%  My research focuses on photogrammetry and 3D reconstruction for territorial and infrastructural monitoring. 
%  My research focuses on UAV-based and terrestrial photogrammetry for land and infrastructure monitoring. I am working on a low-cost image-based system for 4D glacier monitoring (\href{https://github.com/franioli/icepy4d}{ICEpy4D}) and UAV-photogrammetry for structural health assessment and crack detection on concrete bridges.
%  I am contributing to \href{https://github.com/3DOM-FBK/deep-image-matching}{Deep-Image-Matching]} a multiview matching with deep-learning and hand-crafted local features SfM  
 
 \cvevent{2022}{Visiting PhD student (4 months)}{University of Twente, ITC (NL)}{
Development of a deep learning wide-baseline stereo matching workflow for 4D monitoring of an alpine glacier with low-cost time-lapse cameras. 
\href{https://doi.org/10.1007/s41064-023-00272-w}{[Paper]} \href{https://github.com/franioli/icepy4d}{[Code]}
}

\cvevent{2022}{Innsbruck Summer School of Alpine Research}{Obergurgl (AT)}{
Participation in the Summer School \textit{Close Range Sensing Techniques in Alpine Terrain} \href{https://www.uibk.ac.at/iup/buecher/9783991060819.html}{[Proceedings]}
}


\cvevent{2019 - 2020}{Visiting student for MSc Thesis development}{ETH Zürich, VAW (CH)}{
\textit{Evaluation of Airborne Image Velocimetry approaches with low-cost UAVs in riverine environments}. Supervisors: Prof. Livio Pinto{,} Dr. Martin
Detert \href{http://doi.org/10.13140/RG.2.2.36679.65446}{[Thesis]} \href{https://doi.org/10.5194/isprs-archives-XLIII-B2-2020-597-2020}{[Paper]}
}

\cvevent{2017 - 2020}{MSc Environmental and Land Planning Engineering}{Politecnico di Milano}{Major in Land Monitoring and Diagnostics. Grade 110L/110.
}

\cvevent{2019}{Erasmus Exchange}{Aalto University, Helsinki (FIN)}{}

\cvevent{2014 - 2017}{BSc Environmental and Land Planning Engineering}{Politecnico di Milano}{
BSc	Thesis: \textit{Snowpack surveys aimed at hydrological analysis: a case study carried out with UAVs and manual probing measurements on the Belvedere glacier (Macugnaga, Italian Alps)}. Grade 102/110.
}

\vspace{6pt}
\begin{tabular*}{1\mpwidth}{p{0.48\mpwidth}  x{0.50\mpwidth}}
\textcolor{black}{\textbf{Scientific High School}} & \textcolor{complcol}{Liceo Scientifico Falcone e Borsellino}, \textcolor{bgcol}{2009 - 2013} 
\end{tabular*}
\textcolor{softcol}{\hrule}

