\cvsection{Selected pubblications}

\cvlist{\underline{Ioli{,} F.}{,} Dematteis{,} N.{,} Giordan{,} D.{,} 
Nex{,} F. Pinto{,} L.{,} 2024. Deep Learning Low-cost Photogrammetry for 4D Short-term Glacier Dynamics Monitoring. \textit{PFG – Journal of Photogrammetry, Remote Sensing and Geoinformation Science} \href{https://doi.org/10.1007/s41064-023-00272-w}{[Paper]} \href{https://github.com/franioli/icepy4d}{[Code]}}

\cvlist{
\underline{Ioli{,} F.}{,} De Gaetani{,} C.{,} Barbieri{,} F.{,} Gaspari{,} F.{,} Pinto{,} L.{,} Rossi{,} L.{,} 2024. Belvedere Glacier long-term monitoring Open Data (2.0) [Data set]. Zenodo. \href{https://doi.org/10.5281/zenodo.10817029}{[Dataset]} \href{https://thebelvedereglacier.it/}{[Web-app]}
}

\cvlist{
Morelli{,} L.{,} \underline{Ioli{,} F.}{,} Maiwald{,} F.{,} Mazzacca{,} G.{,} Menna{,} F.{,} Remondino{,} F.{,} 2024. Deep-Image-Matching: a Toolbox for Multi-view Image Matching of Complex Scenarios. \textit{Int. Arch. Photogramm. Remote Sens. Spatial Inf. Sci.}{,} XLVIII-2/W4-2024{,} 309–316 \href{https://doi.org/10.5194/isprs-archives-XLVIII-2-W4-2024-309-2024}{[Paper]} \href{https://github.com/3DOM-FBK/deep-image-matching}{[Code]}
}

\cvlist{
Gaspari{,} F.{,} Barbieri{,} F.{,} Fascia{,} R.{,} \underline{Ioli{,} F.}{,} Pinto{,} L.{,} 2024. An Open-Source Web Platform for 3D Documentation and Storytelling of Hidden Cultural Heritage. \textit{Heritage} 7(2){,} 517-536 \href{https://doi.org/10.3390/heritage7020025}{[Paper]} \href{https://github.com/labmgf-polimi/potree-chtemplate}{[Code]}
\href{https://labmgf.dica.polimi.it/pujob/potree-template/}{[Web-app]}
}

\cvlist{Gaspari{,} F.{,} \underline{Ioli{,} F.}{,} Barbieri{,} F.{,} Bonora{,} S.{,} Fascia{,} R.{,} Pinto{,} L.{,} Migliaccio{,} F.{,} 2024. Bridging geomatics theory to real-world applications in alpine surveys through an innovative summer school teaching program. \textit{Int. Arch. Photogramm. Remote Sens. Spatial Inf. Sci.{,}} XLVIII-4/W12-2024{,} 59–66{,} \href{https://doi.org/10.5194/isprs-archives-XLVIII-4-W12-2024-59-2024}{[Paper]}}

\cvlist{
Morelli{,} L.{,} Mazzacca{,} G.{,} Trybała{,} P.{,} Gaspari{,} F.{,} \underline{Ioli{,} F.}{,} Ma{,} Z.{,} Remondino{,} F.{,} Challis{,} K.{,} Poad{,} A.{,} Turner{,} A.{,} and Mills{,} J. P.{,} 2024. The Legacy of Sycamore Gap: The Potential of Photogrammetric AI for Reverse Engineering Lost Heritage with Crowdsourced Data. \textit{Int. Arch. Photogramm. Remote Sens. Spatial Inf. Sci.}{,} XLVIII-2-2024{,} 281–288{,} \href{https://doi.org/10.5194/isprs-archives-XLVIII-2-2024-281-2024}{[Paper]} \href{http://137.117.39.162:10088/}{[Web-app]}
}

\cvlist{
\underline{Ioli{,} F.}{,} Bruno{,} E.{,} Calzolari{,} D.{,} Galbiati{,} M.{,} Mannocchi{,} A.{,} Manzoni{,} P.{,} Martini{,} M.{,} Bianchi{,} A.{,} Cina{,} A.{,} De Michele{,} C.{,} and Pinto{,} L.{,} 2023. A REPLICABLE OPEN-SOURCE MULTI-CAMERA SYSTEM FOR LOW-COST 4D GLACIER MONITORING{,} \textit{Int. Arch. Photogramm. Remote Sens. Spatial Inf. Sci.}{,} XLVIII-M-1-2023{,} 137–144{,} \href{https://doi.org/10.5194/isprs-archives-XLVIII-M-1-2023-137-2023}{[Paper]}
}

\cvlist{
Morelli{,} L.{,} \underline{Ioli{,} F.}{,} Beber{,} R.{,} Menna{,} et al.{,} 2023. COLMAP-SLAM: a Framework for Visual Odometry{,} \textit{Int. Arch. Photogramm. Remote Sens. Spatial Inf. Sci.}{,} XLVIII-1/W1-2023{,} 317–324 \href{https://doi.org/10.5194/isprs-archives-XLVIII-1-W1-2023-317-202}{[Paper]} \href{https://github.com/3DOM-FBK/COLMAP_SLAM}{[Code]}
}

\cvlist{
\underline{Ioli{,} F.}{,} Barbieri{,} F.{,} Gaspari{,} F.{,} Nex{,} F.{,} and Pinto{,} L.{,} 2023. ICEPY4D: A PYTHON TOOLKIT FOR ADVANCED MULTI-EPOCH GLACIER MONITORING WITH DEEP-LEARNING PHOTOGRAMMETRY{,} \textit{Int. Arch. Photogramm. Remote Sens. Spatial Inf. Sci.}{,} XLVIII-1/W2-2023{,} 1037–1044{,} \href{https://doi.org/10.5194/isprs-archives-XLVIII-1-W2-2023-1037-2023}{[Paper]} \href{https://github.com/franioli/icepy4d}{[Code]}
}

\cvlist{
Gaspari{,} F.{,} Barbieri{,} F.{,} Duque{,} J. P.{,} Fascia{,} R.{,} \underline{Ioli{,} F.}{,} Zani{,} G.{,} Carrion{,} D.{,} and Pinto{,} L.{,} 2023. A GEO-DATABASE FOR 3D-AIDED MULTI-EPOCH DOCUMENTATION OF BRIDGE INSPECTIONS{,} \textit{Int. Arch. Photogramm. Remote Sens. Spatial Inf. Sci.}{,} XLVIII-1/W2-2023{,} 299–306{,} \href{https://doi.org/10.5194/isprs-archives-XLVIII-1-W2-2023-299-2023}{[Paper]}
}

\cvlist{
Gaspari{,} F.{,} Barbieri{,} F.{,} Demnati{,} I.{,} \underline{Ioli{,} F.}{,} Pinto{,} L.{,} and Toscani{,} V.{,} 2023. MOBILE MAPPING SOLUTIONS FOR THE UPDATE AND MANAGEMENT OF TRAFFIC SIGNS IN A ROAD CADASTRE FREE OPEN-SOURCE GIS ARCHITECTURE{,} \textit{Int. Arch. Photogramm. Remote Sens. Spatial Inf. Sci.}{,} XLVIII-4/W7-2023{,} 61–66{,} \href{https://doi.org/10.5194/isprs-archives-XLVIII-4-W7-2023-61-2023}{[Paper]}
}

\cvlist{
\underline{Ioli{,} F.}{,} Bianchi{,} A.{,} Cina{,} A.{,} De Michele{,} et al.{,} 2022. Mid-Term Monitoring of Glacier’s Variations with  UAVs: The Example of the Belvedere Glacier. \textit{Remote Sensing} 14{,} 28 \href{https://doi.org/10.3390/rs14010028}{[Paper]} \href{https://zenodo.org/doi/10.5281/zenodo.7842347}{[Open Data]} \href{https://thebelvedereglacier.it/}{[Web Platform]}
}


\cvlist{
\underline{Ioli{,} F.}{,} Pinto{,} A.{,} Pinto{,} L.{,} 2022. UAV-Photogrammetry for Metric Evaluation of Concrete Bridge Cracks. \textit{Int. Arch. Photogramm. Remote Sens. Spatial Inf. Sci.} XLIII-B2-2022{,} 1025–1032 \href{https://doi.org/10.5194/isprs-archives-XLIII-B2-2022-1025-2022}{[Paper]} \href{https://github.com/franioli/Cracks}{[Code]}
}

\cvlist{
Gaspari{,} F.{,} \underline{Ioli{,} F.}{,} Barbieri{,} F.{,} Belcore{,} E.{,} and Pinto{,} L.{,} 2022. INTEGRATION OF UAV-LIDAR AND UAV-PHOTOGRAMMETRY FOR INFRASTRUCTURE MONITORING AND BRIDGE ASSESSMENT{,} \textit{Int. Arch. Photogramm. Remote Sens. Spatial Inf. Sci.}{,} XLIII-B2-2022{,} 995–1002{,} \href{https://doi.org/10.5194/isprs-archives-XLIII-B2-2022-995-2022}{[Paper]}
}

\cvlist{
De Gaetani{,} C.I.{,} \underline{Ioli{,} F.}{,} Pinto{,} L.{,} 2021. Aerial and UAV Images for Photogrammetric Analysis of Belvedere Glacier Evolution in the Period 1977–2019 \textit{Remote Sensing} 13{,} 3787. \href{https://doi.org/10.3390/rs13183787}{[Paper]}
}

\cvlist{
Rossi{,} L.{,} \underline{Ioli{,} F.}{,} Capizzi{,} E.{,} Pinto{,} L.{,} and Reguzzoni{,} M.{,} 2021. IMPROVING UAV TELEMETRY POSITIONING FOR DIRECT PHOTOGRAMMETRY{,} \textit{Int. Arch. Photogramm. Remote Sens. Spatial Inf. Sci.}{,} XLIII-B2-2021{,} 61–68{,} \href{https://doi.org/10.5194/isprs-archives-XLIII-B2-2021-61-2021}{[Paper]}
}

\cvlist{
\underline{Ioli{,} F.}{,} Pinto{,} L.{,} Passoni{,} D.{,} Nova{,} V.{,} Detert{,} M.{,} 2020. Evaluation of Airborne Image Velocimetry approaches using low-cost UAVs in riverine Environments. \textit{Int. Arch. Photogramm. Remote Sens. Spatial Inf. Sci.} Vol.XLIII-B2-2020{,} 597–604 \href{https://doi.org/10.5194/isprs-archives-XLIII-B2-2020-597-2020}{[Paper]}
}